---
title: "Results of 4th Down Predictive and Causal 4th Down Analysis"
output: html_document
---


This section is for notes. The interpretation will be as I go but I want this to be a general outline.

PLAYERS ARE PUT INTO THEIR SLOTS BASED ON SNAP COUNT. THE STARTERS ARE DECIDED ON SNAP COUNT OF THE LAST GAME AND ONLY THE LAST GAME.


* **QB (Slots 1-3):** Quarterbacks. Most plays will only have one QB on the field (slot 1)
* **BACKS (Slots 4-7):** Running backs (RB) and fullbacks (FB).
* **WR (Slots 8-13):** Wide receivers. Teams typically use 2-4 WRs on a given play.
* **TE (Slots 14-16):** Tight ends. These players can act as both receivers and blockers.
* **OL (Slots 17-24):** Offensive line. This includes the center (C), guards (G), and tackles (T). There are usually 5 OL on the field.


* **DL (Slots 1-8):** Defensive line. This includes defensive ends (DE), defensive tackles (DT), and nose tackles (NT). 
* **LB (Slots 9-14):** Linebackers. This can include middle linebackers (MLB), inside linebackers (ILB), and outside linebackers (OLB).
* **CB (Slots 15-19):** Cornerbacks.
* **S (Slots 20-23):** Safeties. This includes free safeties (FS) and strong safeties (SS).

I am gonna place a few experiments here.

Lets run just the vegas number on the conversion and attempt

```{r, include=FALSE}
# Load required library
library(data.table)

# Read the data files
outcome_data <- fread("predict_outcome.csv.gz")
select_data <- fread("predict_select.csv.gz")
ctd1 <- fread("predict_ctd1.csv.gz")

# Create new data.tables with specific variables
select_vegas <- select_data[, .(attempt, vegas_wp, total_line)]
outcome_vegas <- outcome_data[, .(conversion, vegas_wp, total_line)]
ctd1_vegas <- ctd1[, .(conversion, vegas_wp, total_line)]
```

```{r}
# Run OLS models for select_data
model1_select <- lm(attempt ~ vegas_wp, data = select_vegas)
model3_select <- lm(attempt ~ total_line, data = select_vegas)

# Run OLS models for outcome_data
model1_outcome <- lm(conversion ~ vegas_wp, data = outcome_vegas)
model3_outcome <- lm(conversion ~ total_line, data = outcome_vegas)

model1_ctd1 <- lm(conversion ~ vegas_wp, data = ctd1_vegas)
model3_ctd1 <- lm(conversion ~ total_line, data = ctd1_vegas)

# Display summaries
summary(model1_select)
summary(model3_select)
summary(model1_outcome)
summary(model3_outcome)
summary(model1_ctd1)
summary(model3_ctd1)
```

```{r}
```


